Viscous Transport in Eroding Porous Media

### 2019-08-02 docs/transport/erosion_transport.tex
add new figs in transport paper

%\begin{figure}[H]
%\center
%\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top10_268}
%\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of 
%local tortuosity $\tau$ at two neighboring tracers in
% 20 nearly touching bodies eroding when the porosity is 62.9 \% 
%and the tortuosity is 1.0979. The same color of a pair of trajectories 
%means they are from two neighboring tracers.}
%\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/anomalous_diffusion20d_new}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
 20 nearly touching bodies with respect to six porosities. }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{50 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\color{red}
The second nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
}

@@

>>>>

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian}
\caption{\label{fig:Eroding20tort_all} The Eulerian and Lagrangian approach of tortuosity. 
The blue dots are Eulerian approach of tortuosity and the red stars and 
square are Lagrangian approach of tortuosity.}
\end{figure}
%\begin{figure}[H]
%\center
%\includegraphics*[width =0.5\linewidth]{./figs/tort_diff_top10_268}
%\caption{\label{fig:Eroding20tort_traj} The largest 10 difference of 
%local tortuosity $\tau$ at two neighboring tracers in
% 20 nearly touching bodies eroding when the porosity is 62.9 \% 
%and the tortuosity is 1.0979. The same color of a pair of trajectories 
%means they are from two neighboring tracers.}
%\end{figure}

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/anomalous_diffusion20d_new}
\caption{\label{fig:Eroding20anomalous} The analysis of anomalous diffusion in
 20 nearly touching bodies with respect to six porosities.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{50 nearly touching bodies}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\color{red}
The second nearly touching bodies case is 50 bodies in a Hagen-Poiseuille flow.
}

@@

\begin{figure}[H]
\center
\includegraphics*[width =0.5\linewidth]{./figs/tort_eulerian100}
\caption{\label{fig:Eroding100tort_all} The Eulerian and Lagrangian approach of tortuosity. 
The blue dots are Eulerian approach of tortuosity and the red stars and 
square are Lagrangian approach of tortuosity.}
\end{figure}
